Security Audit of Safeplug

### 2014-02-19 report/background.tex

\section{Introduction}
\label{sec:intro}

User privacy is becoming increasingly important as more Internet users realize how vulnerable they are to attackers and eavesdroppers.  This has been exacerbated by the current news about the NSA's surveillance of the Internet~\cite{nsa}.  Unfortunately, the average Internet user is not aware of how to protect themselves against malicious users.

>>>>

\section{Background}
\label{sec:background}
